Knowledge discovery in networked systems

### 2015-08-06 paper.tex
Finish case study of novadelete
Casestudy on novaboot

\begin{itemize}
\item Use SAF to analyze Openstack logs.
  \begin{itemize}
  \item Identify the normal execution logs to explore: osloganal/data/logs/new\_testbed24/novadelete/delete-0.log
  \item Convert the log in JSON into an SQLite3 database. (done)
  \item Convert the log in JSON into an event sqlite3 database required by \saf{}.
    \begin{itemize}
    \item The schema of the database should satisfy the format of the event in
      \saf{}.

@@

      Fix: the problem lie in the file
      ``SAF-trunk/framework/common/sqlutils.py''. In line 76, SAF tests the
      validity of a value by ``if (newv):'', this causes the problem that when
      the value of a field is 0 in dependent events, it will not be
      processed. On the other hand, if the user explicitly specifies the value
      of the field as 0, SAF will convert the value into string ``0'', which
      is accepted by the conditional.
    \item The information extracted from JSON is of coarse granularity. Further
      parsing is needed to obtain detailed information, such as IP addresses,
      device ids.

@@

  \item Obtain domain-specific knowledge about OpenStack and the execution:
    data/models(Filtered Message Sequence)
  \item Specify the domain-specific knowledge in SAF --- on different levels ---
    and found corresponding traces.
    \begin{itemize}
    \item Level 1: event dependency
    \item Level 2: component dependency
    \end{itemize}
  \item Build the causality graph for different levels.
  \end{itemize}
\item Root cause detection of failure symptoms based on the backtracking technique
\end{itemize}

>>>>

\begin{itemize}
\item Use SAF to analyze Openstack logs. All related files can be found under
  ``declarative-log-analytics/codebase/case_study/novaboot''.
  \begin{itemize}
  \item Identify the normal execution logs to explore: osloganal/data/logs/new\_testbed24/novadelete/delete-0.log
  \item Convert the log in JSON into an SQLite3 database. (done)
  \item Convert the log in JSON into an event sqlite3 database required by \saf{}.
    \begin{itemize}
    \item The schema of the database should satisfy the format of the event in
      \saf{}.

@@

      Fix: the problem lies in the file
      ``SAF-trunk/framework/common/sqlutils.py''. In line 76, SAF tests the
      validity of a value by ``if (newv):'', this causes the problem that when
      the value of a field is 0 in dependent events, it will not be
      processed. On the other hand, if the user explicitly specifies the value
      of the field as 0, SAF will convert the value into string ``0'', which
      is accepted by the conditional.
    \item The information extracted from JSON is of coarse granularity. Further
      parse values in the ``message\_body'' to extract OS\_UUID, OS\_IP and
      template id, and store them in the event table.(done)

@@

  \item Obtain domain-specific knowledge about OpenStack and the execution:
    data/models(Filtered Message Sequence)
  \item Understand syntax of \saf{} behavior models
    \begin{itemize}
    \item Read README files
    \item Read the source parser
    \end{itemize}
  \item Specify the domain-specific knowledge in SAF --- on different levels ---
    and found corresponding traces. (done with event-level behavior models)
    \begin{itemize}
    \item Level 1: event dependency
    \item Level 2: component dependency
    \end{itemize}
  \item \sout{Build the causality graph for different levels.}
  \end{itemize}
\item \sout{Root cause detection of failure symptoms based on the backtracking technique}
\end{itemize}

\section{Unsolved problems}
\label{sec:usp}

We list a number of identified but unsolved problems of the project.

\begin{itemize}
\item Results given by \saf{} do not always meet expectation. For example, if a
behavior model specifies chained dependency for a specific field, \saf{} does
not give a sequence of events, but returns the same event for each matched state
model.

\item In the log trace of boot-0.log, the message of template 17 and the message
  of template 15 share the same timestamp. This causes the log trace to match no
  template in the novaboot models. (17 and 15 should be reversed)
